JD notes on effects

### 2022-06-20 manuscript/abstract.tex
How is the title?

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Describing the curves: uncertainty estimation and bias correction for predictions in simple and generalized linear (mixed) models} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Steve Cygu\textsuperscript{1},
Benjamin M. Bolker\textsuperscript{1,2},
Jonathan Dushoff\textsuperscript{1,2}
\\
\bigskip
\textbf{1} School of Computational Science and Engineering, McMaster University, Hamilton, Ontario, Canada
\\
\textbf{2} Department of Biology, McMaster University, Hamilton, Ontario, Canada
\\
\bigskip

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Describing the curves: uncertainty estimation and bias correction for predictions and effects in simple and generalized linear (mixed) models} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Steve Cygu\textsuperscript{1},
Benjamin M. Bolker\textsuperscript{1,2},
Jonathan Dushoff\textsuperscript{1,2}
\\
\bigskip
\textbf{1} School of Computational Science and Engineering, McMaster University, Hamilton, Ontario, Canada
\\
\textbf{2} Department of Biology, McMaster University, Hamilton, Ontario, Canada
\\
\bigskip
